### 2023-07-14 abstract.tex
update

A dissertation submitted for the degree of Doctor of Philosophy in the field of Applied Mathematics (11 - Mathematics and Statistics) - Odessa I.I. Mechnikov National University, Odessa, 2023.

The flat mixed problem of elasticity theory for a finite rectangular domain subjected to various types of loads was considered.
By applying the integral semibound sin- and cos-transformations of Fourier, the initial problem was reduced to a one-dimensional vector boundary problem.
The problem in the transform space was reformulated as a vector boundary problem.
The solution to this problem was constructed as a superposition of the general solution to the homogeneous vector equation and the particular solution to the nonhomogeneous equation.
The solution to the homogeneous vector equation was obtained using matrix differential calculus and represented through the fundamental matrix solution of the corresponding homogeneous matrix equation.
To obtain the particular solution to the nonhomogeneous vector equation, the Green's matrix-function was found using the method of matrix integral transformations. The Green's matrix-function was constructed in the form of a bilinear expansion, which simplifies further computations.
After applying the inverse Fourier transform to the explicit solution of the one-dimensional boundary problem in the transform space and summing weakly convergent integrals in the displacement formulas, only one unknown displacement function along the short end of the semibounded strip remains.
To find this function, a singular integral equation was obtained.
The singular integral equation was solved using the method of orthogonal polynomials.
An investigation of the stress state of the half-strip was conducted for different types of loads and sizes of the rectangular domain.

>>>>

A dissertation submitted for the degree of Doctor of Philosophy in the field of 113 «Applied Mathematics» (11 - «Mathematics and Statistics») - Odessa I.I. Mechnikov National University, Odessa, 2023.

The plane mixed boundary value problems of theory elasticity were solved for an elastic rectangular domain subjected to static and dynamic loads.
By applying the integral finite sin-cos Fourier transformation, the original problem was reduced to a one-dimensional boundary value problem, which was reformulated in the form of a vector boundary value problem.
The solution to this problem was constructed as a superposition of the general solution of the homogeneous vector equation and the particular solution of the nonhomogeneous equation.
The solution of the homogeneous vector equation was obtained using matrix differential calculus and represented using the fundamental matrix solution system of the corresponding homogeneous matrix equation.
The particular solution of the nonhomogeneous vector equation was found using the Green's matrix function representation.
The application of inverse Fourier transformation and the realization of the separation of weakly convergent parts of the integral provide the field of displacements and stresses through an unknown function - the boundary value of displacements along the end of the rectangular region.
To find this function under the boundary condition, a singular integral equation was derived and solved using the method of orthogonal polynomials.
The stress state of the medium was investigated for various types of loading and different geometric dimensions of the rectangular region.
